### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@88d3f1a8d524d165e589917fe8549b8c7c979ccd 🚀

The first result is using a log-normal distribution of relative
abundance (Hubbell 2001) to compute a null expectation of the number of
total observations of individuals of \emph{any species} by simulating
the process of observation on food-webs generated using the niche model
(\textbf{williamsmart?}) with connectance parameterized by the
flexible-links model (\textbf{cite?}). An example of this relation for
networks with varying spceies richness is shown in fig.~\ref{fig:fnr}.

@@

@@

>>>>

The first result is using a log-normal distribution of relative
abundance (Hubbell 2001) to compute a null expectation of the number of
total observations of individuals of \emph{any species} by simulating
the process of observation on food-webs generated using the niche model
(Williams \& Martinez 2000) with connectance parameterized by the
flexible-links model (MacDonald \emph{et al.} 2020). An example of this
relation for networks with varying spceies richness is shown in
fig.~\ref{fig:fnr}.

@@

\leavevmode\hypertarget{ref-MacDonald2020RevLin}{}%
MacDonald, A.A.M., Banville, F. \& Poisot, T. (2020). Revisiting the
Links-Species Scaling Relationship in Food Webs. \emph{Patterns}, 1.

@@

\leavevmode\hypertarget{ref-Williams2000SimRul}{}%
Williams, R.J. \& Martinez, N.D. (2000). Simple rules yield complex food
webs. \emph{Nature}, 404, 180--183.
